Visualizations for the manuscript

### 2022-03-14 metanalysis_visualization/manuscript_Figures.Rmd
Minor changes

install_github("jokergoo/ComplexHeatmap")
install_github("teunbrand/ggh4x")

library( ComplexHeatmap)
library( ggh4x )
```

@@

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(i)
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    table1_all <- table1
  } else {
    count_icd_all <- rbind(count_icd_all, count_icd)
    patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <- rbind(bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <- rbind(bootstrapped_coefficients_all, bootstrapped_coefficients_df)
   mental_codes_qc_output <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all, mental_codes_qc_output)
    table1_all <- rbind( table1_all, table1)
    }
  rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
     perc_disorder_group,ratios_patients_with_without_psy,
     patient_count_psy_period_psy_clear, bootstrapped_coefficients_df,
     bootstrapped_fitted_df, mental_codes_qc_output, table1)
}
```

@@

```{r, results='hide'}
sessionInfo()
```

>>>>

if (! "ComplexHeatmap" %in% rownames(installed.packages())) install_github("jokergoo/ComplexHeatmap")
if (! "ggh4x" %in% rownames(installed.packages())) install_github("teunbrand/ggh4x")
library( ComplexHeatmap)
library( ggh4x )
```

@@

Put all the aggregated counts from the different sites together
```{r}
for( i in 1:length( outputFiles )){
  print(i)
  load(paste0( outputDir, outputFiles[i]))
  if( i == 1 ){
    count_icd_all <- count_icd
    patients_hospitalized_agg_sex_perc_all <- patients_hospitalized_agg_sex_perc
    patient_count_psy_period_psy_all <- patient_count_psy_period_psy
    perc_disorder_group_all <- perc_disorder_group
    ratios_patients_with_without_psy_all <- ratios_patients_with_without_psy
    bootstrapped_fitted_all <- bootstrapped_fitted_df
    bootstrapped_coefficients_all <- bootstrapped_coefficients_df
    mental_codes_qc_output_all <- mental_codes_qc_output %>%
      select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
    table1_all <- table1
  } else {
    if (outputFiles[i] == "peds_psy_aggResults_CHOP.RData") {
      count_icd_all <- tryCatch(
        rbind(count_icd_all, count_icd),
        error = function(e) count_icd_all
      )
      patients_hospitalized_agg_sex_perc_all <- tryCatch( 
        rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc),
        error = function(e) patients_hospitalized_agg_sex_perc_all
      )
      perc_disorder_group_all <- tryCatch(
        rbind(perc_disorder_group_all, perc_disorder_group),
        error = function(e) perc_disorder_group_all
      )
      mental_codes_qc_output_all <- tryCatch(
        rbind( mental_codes_qc_output_all,
               mental_codes_qc_output %>%
                 select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
        ),
        error = function(e) mental_codes_qc_output_all
      )
      table1_all <- table1_all
    } else {
      count_icd_all <- rbind(count_icd_all, count_icd)
      perc_disorder_group_all <- rbind(perc_disorder_group_all, perc_disorder_group)
      patients_hospitalized_agg_sex_perc_all <- rbind( patients_hospitalized_agg_sex_perc_all, patients_hospitalized_agg_sex_perc)
      mental_codes_qc_output_all <- rbind( mental_codes_qc_output_all,
                                           mental_codes_qc_output %>%
                                             select( disorder_group, description, concept_code, distinct_patients, distinct_observations, siteid )
      )
      table1_all <- rbind( table1_all, table1)
    }
    patient_count_psy_period_psy_all <- rbind( patient_count_psy_period_psy_all,patient_count_psy_period_psy)
    ratios_patients_with_without_psy_all <- rbind( ratios_patients_with_without_psy_all, ratios_patients_with_without_psy)
    bootstrapped_fitted_all <- rbind(bootstrapped_fitted_all, bootstrapped_fitted_df)
    bootstrapped_coefficients_all <- rbind(bootstrapped_coefficients_all, bootstrapped_coefficients_df)
    rm(count_icd,patients_hospitalized_agg_sex_perc,patient_count_psy_period_psy,
       perc_disorder_group,ratios_patients_with_without_psy,
       patient_count_psy_period_psy_clear, bootstrapped_coefficients_df,
       bootstrapped_fitted_df, mental_codes_qc_output, table1)
  }
}

@@

```{r, results='hide'}
sessionInfo()
